Displacement of fishing effort by Large Scale Marine Protected Areas[^*]

### 2018-10-20 docs/Manuscript.tex
Obtained monthly treatment level rasters and updated ms

Four our empirical identification we calculated the proportion of
fishing effort allocated every month to each spatially explicit regions
defined in section \ref{methods}. For purse seiners, these represent 9
main EEZs, PIPA, the high seas, and a group of other EEZs. Figure
\ref{fig:redist_trend_ps} shows the monthly relative fishing hours that
each region received by all 61 treated vessels. The top-left panel shows
the change in fishing effort inside PIPA, including the preemptive
fishing and immediate reduction previously reported
\citep{mcdermott_2018}. The change in the relative allocation of fishing
effort by purse seiners increases in eight of the 12 regions after PIPA
implementation (Table \ref{tab:disp_mod}, fig:map\_change\_ps). The
largest increase is observed for the I-Kiribati EEZ, with an average
increase of 0.11 (\emph{p \textless{} 0.001}). In other words, the
redistribution of treated vessels caused a 10\% increase in the
\emph{relative} allocation of fishing effort within I-Kiribati waters.
The only decrease is observed for Papua New Guinea, but the coefficient
is not significant.

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

\caption{\label{tab:unnamed-chunk-16}\label{tab:disp_mod}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
\centering
\begin{tabular}[t]{ll}
\toprule
term & h\_prop\\
\midrule
(Intercept) & 0.087 (0.002)***\\
post & -0.081 (0.003)***\\
sate2 & -0.003 (0.001)***\\
sate3 & -0.002 (0.001)\\
post:countryEEZ COK 1 & 0.088 (0.002)***\\
\addlinespace
post:countryEEZ FSM 1 & 0.091 (0.003)***\\
post:countryEEZ KIR 1 & 0.081 (0.003)***\\
post:countryEEZ KIR 2 & 0.127 (0.004)***\\
post:countryEEZ KIR 3 & 0.055 (0.005)***\\
post:countryEEZ MHL 1 & 0.078 (0.003)***\\
\addlinespace
post:countryEEZ NRU 1 & 0.083 (0.003)***\\
post:countryEEZ PNG 2 & -0.008 (0.005)*\\
post:countryEEZ SLB 1 & 0.114 (0.004)***\\
post:countryEEZ TUV 1 & 0.095 (0.003)***\\
post:countryHS & 0.122 (0.003)***\\
\addlinespace
post:countryHS COK 1 & 0.083 (0.002)***\\
post:countryHS KIR 1 & 0.112 (0.003)***\\
post:countryHS KIR 2 & 0.093 (0.002)***\\
post:countryHS KIR 3 & 0.108 (0.003)***\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
and treatment. Control group is japanese vessels.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
year-month and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
year-month and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
year-month and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
year-month and treatment. Control group is japanese vessels.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
\caption{\label{fig:unnamed-chunk-28}\label{fig:fishing_raster_full}}
\end{figure}

>>>>

For our empirical identification we \ldots{} The XXX shows the change in
fishing effort inside PIPA, including the preemptive fishing and
immediate reduction previously reported \citep{mcdermott_2018}. The
change in the relative allocation of fishing effort by purse seiners
increases for most regions after PIPA implementation (Table
\ref{tab:disp_mod}, \ref{fig:mean_change}). The largest increase is
observed for the I-Kiribati EEZ, with an average increase of 0.11
(\emph{p \textless{} 0.001}). In other words, the redistribution of
treated vessels caused a 10\% increase in the \emph{relative} allocation
of fishing effort within I-Kiribati waters. The only decrease is
observed for Papua New Guinea, but the coefficient is not significant.

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:mean_change}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
\caption{\label{fig:unnamed-chunk-16}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-19-1.pdf}
\caption{\label{fig:unnamed-chunk-19}\label{fig:q1}Interaction of quarters
and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
\caption{\label{fig:unnamed-chunk-20}\label{fig:q2}Interaction of quarters
and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
\caption{\label{fig:unnamed-chunk-21}\label{fig:q3}Interaction of quarters
and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
\caption{\label{fig:unnamed-chunk-22}\label{fig:q4}Interaction of quarters
and treatment. Control group is japanese vessels.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
\caption{\label{fig:unnamed-chunk-23}\label{fig:ym1}Interaction of
year-month and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
\caption{\label{fig:unnamed-chunk-24}\label{fig:ym2}Interaction of
year-month and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:ym3}Interaction of
year-month and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
\caption{\label{fig:unnamed-chunk-26}\label{fig:ym4}Interaction of
year-month and treatment. Control group is japanese vessels.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
\caption{\label{fig:unnamed-chunk-27}\label{fig:fishing_raster_full}}
\end{figure}

### 2018-10-20 rmd/Manuscript.Rmd
Obtained monthly treatment level rasters and updated ms

```{r, fig.cap = "\\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest. A solid line indicates countries that belong to the PNA, while a dashed line indicates all others. A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA."}
countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI")

@@

Regressions coefficients for our DiD analysis are shown in Table \ref{tab:did}. Columns 1 -3 use all data for controls. Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels. Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs to avoid perfect colinearity between Japanese flag and control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}. It must be noted, however, that when reducing the linear structure of the $Pre \times Post$ design and instead interacting the treatment dummy with quarterly or year-month combinations we are not able to reject the null hypotheses of no change (Figures \ref{fig:q1,fig:q2,fig:q3,fig:q4,fig:ym1,fig:ym2,fig:ym3,fig:ym4}).

@@

Four our empirical identification we calculated the proportion of fishing effort allocated every month to each spatially explicit regions defined in section \ref{methods}. For purse seiners, these represent 9 main EEZs, PIPA, the high seas, and a group of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly relative fishing hours that each region received by all `r pipa_vessels` treated vessels. The top-left panel shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}. The change in the relative allocation of fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation (Table \ref{tab:disp_mod}, fig:map_change_ps). The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*). In other words, the redistribution of treated vessels caused a 10\% increase in the *relative* allocation of fishing effort within I-Kiribati waters. The only decrease is observed for Papua New Guinea, but the coefficient is not significant.

@@

fishing_raster <- readRDS(here::here("data", "fishing_raster_BACI.rds"))

fishing_raster %>% 
  filter(between(year, 2013, 2016)) %>% 
  ggplot() +
  geom_raster(mapping = aes(x = lon, y = lat, fill = hours_norm)) +
  geom_sf(data = eez, fill = "transparent", color = "black") +
  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
  # geom_sf(data = small_coast, color = "black") +
  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
  scale_fill_viridis_c(trans = "log10") +
  facet_grid(year~treated, switch = "y") +
  # coord_equal() +
  ggtheme_map() +
  theme(legend.position = "bottom")
```

@@

```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
HS_disp_poly <- matrix(c(200, 10, 210, 10 ,210 ,20 ,200 ,20 ,200, 10),
                  ncol=2,
                  byrow=TRUE) %>%
  list() %>%
  st_polygon() %>% 
  st_sfc(crs = "+proj=longlat +datum=WGS84 +no_defs")

HS_disp <- data.frame(country = "HS",
                      PNA = F) %>% 
  st_set_geometry(HS_disp_poly) %>% 
  mutate(id = country, source = country, PNA = F) %>% 
  select(id, source, PNA, country)

eezs_exclude <- c("HS MUS 1", "EEZ MUS 1", "EEZ MDG 1", "EEZ MDG 2", "HS MDG 1", "HS MDG 2", "HS MOZ 1", "EEZ MOZ 1")

regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
               layer = "regions")

# I AM EXCLUDING MUS WHICH SHOULD BE PUT INTO EEZ
regions %>% 
  rbind(HS_disp) %>% 
  left_join(ba_disp, by = c("id" = "country")) %>%
  filter(!id %in% eezs_exclude) %>%
  ggplot() +
  geom_sf(aes(fill = change), color = "black") +
  ggtheme_plot() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
```

```{r, results = "asis"}
disp_mod_ps_data <- displacement_data %>% 
  filter(!is.na(country),
         gear == "purse_seines",
         !country %in% regions_few_points) %>% 
  mutate(post = post *1,
         year2 = year^2,
         month_c = as.character(month),
         country = fct_relevel(country, "PIPA PIPA 1"),
         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
                          date > lubridate::date("2015/12/31") ~ "3",
                          T ~ "2"))

disp_mod_ps1 <- lm(h_prop ~ post*country + sate, data = disp_mod_ps_data)

commarobust::commarobust_tidy(disp_mod_ps1) %>% 
  mutate(b = str_detect(term, "Intercept"),
         c = str_detect(term, "post"),
         d = str_detect(term, "sate"),
         a = b*c,
         p1 = ifelse(p < 0.1, "*", ""),
         p2 = ifelse(p < 0.05, "*", ""),
         p3 = ifelse(p < 0.01, "*", ""),
    h_prop = paste0(formatC(est, digits = 3, format = "f"),
                    " (",
                    formatC(se, digits = 3, format = "f"),
                    ")",
                    p1,
                    p2,
                    p3)) %>% 
  filter(b+c+d > 0) %>% 
  select(term, h_prop) %>% 
  knitr::kable(booktabs = T,
               caption = "\\label{tab:disp_mod}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")

```

@@

```{r, results = "asis"}
model_data <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>%
  filter(year < 2018,
         baci_strict,
         gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1,
         mmsi_c = as.factor(mmsi))

m1 <- lm(hours ~ post*treated, data = model_data)
m2 <- lm(hours ~ post*treated + month_c, data = model_data)
m3 <- lm(hours ~ post*treated + month_c + year_c, data = model_data)
m4 <- lm(hours ~ post*treated + month_c + year_c + flag, data = model_data)

models <- list(m1, m2, m3, m4)

@@

```{r, fig.width = 7, fig.height = 10.5, fig.cap = "\\label{fig:fishing_raster_full}"}
ggplot() +
  geom_raster(data = fishing_raster, mapping = aes(x = lon, y = lat, fill = hours_norm)) +
  geom_sf(data = eez, fill = "transparent", color = "black") +
  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
  geom_sf(data = small_coast, color = "black") +
  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
  scale_fill_viridis_c(trans = "log10") +
  facet_grid(year~treated, switch = "y") +
  # coord_equal() +
  ggtheme_map() +
  theme(legend.position = "bottom")
```

>>>>

```{r, fig.cap = "\\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest. A solid line indicates countries that belong to the PNA, while a dashed line indicates all others. A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA."}
countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI"< "FJI")

@@

Regressions coefficients for our DiD analysis are shown in Table \ref{tab:did}. Columns 1 -3 use all data for controls. Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels. Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs to avoid perfect colinearity between Japanese flag and control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}. It must be noted, however, that when reducing the linear structure of the $Pre \times Post$ design and instead interacting the treatment dummy with quarterly or year-month combinations we are not able to reject the null hypotheses of no change (Figures \ref{fig:q1}-\ref{fig:ym4}).

@@

For our empirical identification we ... The XXX shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}. The change in the relative allocation of fishing effort by purse seiners increases for most regions after PIPA implementation (Table \ref{tab:disp_mod}, \ref{fig:mean_change}). The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*). In other words, the redistribution of treated vessels caused a 10\% increase in the *relative* allocation of fishing effort within I-Kiribati waters. The only decrease is observed for Papua New Guinea, but the coefficient is not significant.

@@

fishing_raster <- readRDS(file = here::here("data", "rasterized_effort_by_region.rds"))

fishing_raster %>% 
  filter(between(year, 2013, 2016)) %>% 
  ggplot() +
  geom_raster(mapping = aes(x = x, y = y, fill = hours_norm)) +
  geom_sf(data = eez, fill = "transparent", color = "black") +
  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
  geom_sf(data = small_coast, color = "black") +
  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
  scale_fill_viridis_c(trans = "log10") +
  facet_grid(year~treated, switch = "y") +
  # coord_equal() +
  ggtheme_map() +
  theme(legend.position = "bottom")
```

@@

```{r, fig.cap = "\\label{fig:mean_change}"}
raster_month_region <- readRDS(file = here::here("data", "monthly_rasterized_effort_by_region.rds"))

model <- lm(hours ~ year_c * id, data = raster_month_region)

pd <- position_dodge(width = 0.2)

commarobust::commarobust_tidy(model) %>%
  filter(str_detect(term, ":")) %>%
  mutate(year = as.numeric(str_extract(term, "[:digit:]+")),
         term = str_extract(term, pattern = "[:alpha:]+ [:alpha:]+ [:digit:]"),
         p = ifelse(p < 0.05, "p < 0.05", "p > 0.05")) %>%
  ggplot(aes(x = year, y = est, color = term)) +
  geom_errorbar(aes(ymin = est - se, ymax = est + se), width = 0, position = pd, size = 1) +
  geom_point(aes(shape = p), size = 2, position = pd) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ggtheme_plot() +
  guides(color = guide_legend(ncol = 2, order = 2),
         shape = guide_legend(order = 1))
```

@@

```{r}
model_data <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>%
  filter(year < 2018,
         baci_strict,
         gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1,
         mmsi_c = as.factor(mmsi))

m1 <- lm(hours ~ post*treated, data = model_data)
m2 <- lm(hours ~ post*treated + month_c, data = model_data)
m3 <- lm(hours ~ post*treated + month_c + year_c, data = model_data)
m4 <- lm(hours ~ post*treated + month_c + year_c + flag, data = model_data)
```

```{r, results = "asis"}
models <- list(m1, m2, m3, m4)

@@

```{r, fig.width = 7, fig.height = 10.5, fig.cap = "\\label{fig:fishing_raster_full}"}
ggplot() +
  geom_raster(data = fishing_raster, mapping = aes(x = x, y = y, fill = hours_norm)) +
  geom_sf(data = eez, fill = "transparent", color = "black") +
  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
  geom_sf(data = small_coast, color = "black") +
  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
  scale_fill_viridis_c(trans = "log10") +
  facet_grid(year~treated, switch = "y") +
  # coord_equal() +
  ggtheme_map() +
  theme(legend.position = "bottom")
```
